  %%%%%%%%%%%%%%%%%
  % This is an example CV created using altacv.cls (v1.1.5, 1 December 2018) written by
  % LianTze Lim (liantze@gmail.com), based on the
  % Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
  %
  %% It may be distributed and/or modified under the
  %% conditions of the LaTeX Project Public License, either version 1.3
  %% of this license or (at your option) any later version.
  %% The latest version of this license is in
  %%    http://www.latex-project.org/lppl.txt
  %% and version 1.3 or later is part of all distributions of LaTeX
  %% version 2003/12/01 or later.
  %%%%%%%%%%%%%%%%

  %% If you are using \orcid or academicons
  %% icons, make sure you have the academicons
  %% option here, and compile with XeLaTeX
  %% or LuaLaTeX.
  % \documentclass[10pt,a4paper,academicons]{altacv}

  %% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
  % \documentclass[10pt,a4paper,normalphoto]{altacv}

  \documentclass[10pt,a4paper,ragged2e]{altacv}

  %% AltaCV uses the fontawesome and academicon fonts
  %% and packages.
  %% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

  % Change the page layout if you need to
  \geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1cm}

  % Change the font if you want to, depending on whether
  % you're using pdflatex or xelatex/lualatex
  \ifxetexorluatex
    % If using xelatex or lualatex:
    \setmainfont{Carlito}
  \else
    % If using pdflatex:
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[default]{lato}
  \fi

  % Change the colours if you want to
  \definecolor{VividPurple}{HTML}{3E0097}
  \definecolor{SlateGrey}{HTML}{2E2E2E}
  \definecolor{LightGrey}{HTML}{666666}
  \colorlet{heading}{VividPurple}
  \colorlet{accent}{VividPurple}
  \colorlet{emphasis}{SlateGrey}
  \colorlet{body}{LightGrey}

  % Change the bullets for itemize and rating marker
  % for \cvskill if you want to
  \renewcommand{\itemmarker}{{\small\textbullet}}
  \renewcommand{\ratingmarker}{\faCircle}

  \addbibresource{sample.bib}

  \pdfmapfile{+fontawesome5.map}




  \begin{document}

  \name{\huge Mehtab Zafar}
  \tagline{Information Security / Software Development}
  \personalinfo{%
    \hspace{1.3cm}\email{\normalsize hello@mzfr.me}\hspace{1.33cm}\linkedin{\normalsize \href{https://www.linkedin.com/in/mzfr/}{linkedin.com/in/mzfr/}}

    \hspace{1.3cm}{\normalsize\href{https://hackerone.com/mzfr}{hackerone.com/mzfr}} \hspace{1.5cm}\github{\normalsize github.com/mzfr}
  }

  \begin{fullwidth}
  \makecvheader
  \end{fullwidth}

  \AtBeginEnvironment{itemize}{\small}

  \cvsection[page1sidebar]{Work Experience}
  \cvevent{BugBounty}{Hackerone / Bugcrowd / Initgriti}{Aug 2020 -- ongoing}{Independent/Remote}

  \begin{itemize}

  \item Reported bugs to several Fortune 500 companies.
  \item Focusing mostly on Web and Mobile application related vulnerabilities.
  \item Hall of Fame in companies like GitHub, PayPal, US Department of Defense, DELL, Atlassian, Zynga etc

  \end{itemize}

  \divider

  \cvevent{Developer}{The Honeynet Project {\hspace{0.5cm}\color{accent} \faGithub \href{https://github.com/mushorg/tanner/commits?author=mzfr}{\small \normalfont \hspace{1mm}Code}}}{May 2020 -- August 2020}{Google Summer of Code}
  \begin{itemize}
  \item Made improvement in a high interaction honeypot (Snare/Tanner)

  \item Added support for persistent storage using PostgreSQL and SQLAlchemy
  
  \item Improved the API functionality based on the new database structure

  \item Improved cloning functionality using Selenium/Chrome headless browser

  \end{itemize}

  \divider

  \cvevent{Mentor}{MetaBrainz Foundation}{Dec 2019 -- Jan 2020}{Google Code-In}
  \begin{itemize}

  \item Mentored students from all over the globe on various python projects under the MetaBrainz Foundation.

  \end{itemize}

  \divider

  \cvevent{Content Creator}{Vulnhub / TryHackMe}{Aug 2019 -- March 2020}{Independent/Remote}
  \begin{itemize}
  \item Created various CaptureTheFlag (CTF) challenges for \href{https://tryhackme.com/p/falconfeast}\emp{TryHackme.com}} that teaches about Web related vulnerability like XXE, XSS, JWT etc

  \item Created a bunch of potential Vulnerable machines for \href{https://www.vulnhub.com/series/djinn,260/}\emp{VulnHub.com}}
  
  \item Beta tested various vulnerable virtual machines like TempusFugit series, DC8 for vulnhub.com.

  \end{itemize}

  \divider

  \cvevent{Developer}{XBMC Foundation {\hspace{0.5cm}\color{accent} \faGithub \href{https://github.com/xbmc/addon-check/commits?author=mzfr}{\small \normalfont \hspace{1mm}Code}}}{May 2018 -- Aug 2018}{Google Summer of Code}
  \begin{itemize}

  \item Worked on an Open source project under a student program by Google.

  Developed a tool for performing static code analysis on all addons for Kodi.

  \end{itemize}


  \cvsection{Projects}

  \begin{itemize}
  \item {\color{black} \normalsize \textbf{slicer}} \hfill {\color{accent} \faGithub \href{https://github.com/mzfr/slicer}{ \hspace{0.5mm}Code}}

  A tool that helps in automating the reconnaissance process of Android Package (APK) file. It can show vulnerable activities, receivers and services.

  \divider

  \item {\color{black} \normalsize \textbf{liffy}} \hfill {\color{accent} \faGithub \href{https://github.com/liffy}{ \hspace{0.5mm}Code}}

  A tool to automate the process of discovering and exploiting Local file inclusion attack

  \divider

  \item {\color{black} \normalsize \textbf{gtfo}} \hfill {\color{accent} \faGithub \href{https://github.com/gtfo}{ \hspace{0.5mm}Code}}

  A tool to help you search exploits for various Linux and Windows binaries which can then be used to escalate privileges

  \divider

  \item {\color{black} \normalsize \textbf{cowrie}} \hfill {\color{accent} \faGithub \href{https://github.com/cowrie/cowrie/commits?author=mzfr}{ \hspace{0.5mm}Code}}

  Added support for plugins like DNS reverse lookup, greynoise etc. into SSH, FTP, Telnet based high interaction honeypot.


  \end{itemize}

  \clearpage

  \end{document}
